---
title: "Seattle Airbnb Report"
author: "Christina Stanfield"
date: "2/19/2020"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(knitr)
source("./analysis.R")

```

This is some text outside of a code chunk. It's just regular **Markdown** text without any code, which is good for writing lots of stuff.

## Seattle Airbnbs

There are `r total_listings` Airbnb listings in Seattle.
The average price of an Airbnb in Seattle is $`r avg_price`.
There are `r total_reviews` reviews written about Airbnbs in Seattle.

## Interactive Map of Prices of Airbnbs in the UDistrict

```{r echo=FALSE, warning=FALSE}

price_map

```

## Graph of Maximum Listing Price by Neighborhod

```{r echo=FALSE, warning=FALSE}

max_price_graph

```

## Graph of Avg Number Reviews Written per Listing by Neighborhood

```{r echo=FALSE, warning=FALSE}

avg_reviews_graph

```

## Summary Table of Average Prices Per Neighborhood

```{r echo=FALSE, warning=FALSE}

kable(price_table,
      row.names = FALSE,
      col.names = c("Neighborhood", "Average Price"))

```

